% ------------------------------------------------------------------------------
% The acknowledgement section of a thesis is where you recognise and thank
% those who supported you. This can be but is not limited to individuals,
% institutions or organisations.
% ------------------------------------------------------------------------------

\chapter*{Acknowledgements}
\markboth{Acknowledgements}{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}


% -- Your text goes here --
This master's thesis would not have been written over five months without the support of a number of people. It's time to thank all these contributors, whether they are closely involved in the project or are far removed from the digital world.

\begin{itemize}
    \item [•] First of all, I would like to thank my family and especially my parents, without whom I wouldn't be able to fulfil all my dreams. So I'm always able to fulfil my potential in my daily life. It's the strength of spirit I've inherited that will always enable me to move forward despite the obstacles I encounter.
    \item [•] I would also like to express my deep gratitude to my supervisor, Mr Fabien Vannel, who was always available at any time. His sound advice was invaluable throughout this work, making a significant contribution to achieving the desired end result.
    \item [•] Finally, I would like to express my sincere thanks to everyone at \nameref{subsec:56k.cloud}. Their exceptional team brought joy and good humour to the organisation. Their invaluable contribution in sharing their knowledge has been invaluable when obstacles have been encountered. In addition, my professional experience has been enriched by my involvement with the company, and I've had the opportunity to take part in a number of enriching events. I'm also grateful for the opportunity to take the AWS Certified Cloud Practitioner course.
\end{itemize}