% ------------------------------------------------------------------------------
% Terms
% -----
% format:  \newglossaryentry{<label>}{<settings>}
% example: \newglossaryentry{computer}
%{
%	name=computer,
%	description={is a programmable machine that receives input, stores and manipulates data, and provides output in a useful format}
%}
% Development
% ------------------------------------------------------------------------------

\newglossaryentry{cloud}{
    name=cloud,
    description={The term cloud refers to a remote infrastructure made up of servers that can be accessed from anywhere in the world via an internet connection}
}

\newglossaryentry{cloud_infrastructure}{
    name=cloud infrastructure,
    description={A cloud infrastructure is the set of computing resources in the cloud that make up an IT environment. This includes servers, storage, network and security}
}

\newglossaryentry{arm}{
    name=Arm,
    description={Arm is a British company that designs processors with RISC-type (Reduced Instruction Set Computer) architectures}
}

\newglossaryentry{aws}{
    name=AWS,
    description={AWS stands for Amazon Web Services. It is a company that provides a cloud platform with over 200 services. The resources are spread over more than 32 regions around the world}
}

\newglossaryentry{provisioning}{
    name=provisioning,
    description={Provisioning means the automated creation and installation of an IT infrastructure. Device provisioning involves creating the resources needed to integrate it into an IT infrastructure and integrating it into the existing infrastructure}
}

\newglossaryentry{work_package}{
    name=work package,
    description={In project management, work packages are commonly used to define a plan. The plan provides an overview of the progress of the project}
}

\newglossaryentry{hes}{
    name=HES-SO,
    description={The HES-SO is a Swiss university based in French-speaking Switzerland. It offers a wide range of specialisations in different fields such as technology, health, social work, economics and art. It has several buildings spread across the French-speaking cantons}
}

\newglossaryentry{scrum}{
    name=Scrum,
    description={Scrum is a process framework based on agile methodology for software engineering. It is suitable for small development teams. It ensures good communication between the customer and the team. It enables the first versions of a software product to be delivered quickly.}
}

\newglossaryentry{kanban}{
    name=KanBan,
    description={KanBan is a project management tool designed to efficiently manage a workflow over a given period. It is widely adopted in agile methodology}
}


% ------------------------------------------------------------------------------
% Acronyms
% --------
% format:  \newacronym{<label>}{<abbrv>}{<full>}
% example: \newacronym{lvm}{LVM}{Logical Volume Manager}
% plural:  \newacronym[longplural={Frames per Second}]{fpsLabel}{FPS}{Frame per Second}
% ------------------------------------------------------------------------------

\newacronym{devops}{DevOps}{\textbf{D}evelopment and \textbf{O}perations}

\newacronym{iot}{IoT}{\textbf{I}nternet \textbf{o}f \textbf{T}hings}

\newacronym{ci}{CI}{\textbf{C}ontinuous \textbf{I}ntergration}

\newacronym{cd}{CD}{\textbf{C}ontinuous \textbf{D}elivery}

\newacronym{po}{PO}{\textbf{P}roduct \textbf{O}wner}

\newacronym{roi}{ROI}{\textbf{R}eturn \textbf{O}n \textbf{OI}nvestment}

\newacronym{wip}{WIP}{\textbf{W}ork \textbf{I}n \textbf{P}rogress}

\newacronym{iaas}{IaaS}{\textbf{I}nfrastructure \textbf{a}s \textbf{a} \textbf{S}ervice}

\newacronym{paas}{PaaS}{\textbf{P}latform \textbf{a}s \textbf{a} \textbf{S}ervice}

\newacronym{saas}{SaaS}{\textbf{S}oftware \textbf{a}s \textbf{a} \textbf{S}ervice}

\newacronym{iac}{IaC}{\textbf{I}nfrastructure \textbf{a}s \textbf{C}ode}

\newacronym{ec2}{EC2}{\textbf{E}lastic \textbf{C}ompute \textbf{C}loud}

\newacronym{ble}{BLE}{\textbf{B}luetooth \textbf{L}ow \textbf{E}nergy}

\newacronym{wifi}{WiFi}{\textbf{Wi}reless \textbf{Fi}delity}

\newacronym{mqtt}{MQTT}{\textbf{M}essage \textbf{Q}ueuing \textbf{T}elemetry \textbf{T}ransport}

\newacronym{coap}{CoAP}{\textbf{Co}nstrained \textbf{A}pplication \textbf{P}rotocol}

\newacronym{http}{HTTP}{\textbf{H}yper\textbf{T}ext \textbf{T}ransfer \textbf{P}rotocol}

\newacronym{rest}{REST}{\textbf{RE}presentational \textbf{S}tate \textbf{T}ransfer}

\newacronym{udp}{UDP}{\textbf{U}ser \textbf{D}atagram \textbf{P}rotocol}

\newacronym{soa}{SOA}{\textbf{S}ervice-\textbf{O}riented \textbf{A}rchitecture}

\newacronym{tcp}{TCP}{\textbf{T}ransmission \textbf{C}ontrol \textbf{P}rotocol}

\newacronym{nas}{NAS}{\textbf{N}etwork \textbf{A}ttached \textbf{S}torage}

\newacronym{api}{API}{\textbf{A}pplication  \textbf{P}rogramming \textbf{I}nterface}

\newacronym{cdk}{CDK}{\textbf{C}loud \textbf{D}evelopment \textbf{K}it}

\newacronym{a_arm}{ARM}{\textbf{A}zure \textbf{R}esource \textbf{M}anager}

\newacronym{sdk}{SDK}{\textbf{S}oftware \textbf{D}evelopment \textbf{K}it}

\newacronym{json}{JSON}{\textbf{J}ava\textbf{S}cript \textbf{O}bject \textbf{N}otation}

\newacronym{nat}{NAT}{\textbf{N}etwork \textbf{A}ddress \textbf{T}ranslation}

\newacronym{ota}{OTA}{\textbf{O}ver-\textbf{T}he-\textbf{A}ir}

\newacronym{qos}{QoS}{\textbf{Q}uality \textbf{o}f \textbf{S}ervice}

\newacronym{cli}{CLI}{\textbf{C}ommand \textbf{L}ine \textbf{i}nterface}

\newacronym{bsa}{BSA}{\textbf{B}ase \textbf{S}ystem \textbf{A}rchitecture}

\newacronym{bbr}{BBR}{\textbf{B}ase \textbf{B}oot \textbf{R}quirements}

\newacronym{os}{OS}{\textbf{O}perating \textbf{S}ystem}

\newacronym{bsd}{BSD}{\textbf{B}erkeley \textbf{S}oftware \textbf{D}istribution}

\newacronym{csr}{CSR}{\textbf{C}ertificate \textbf{S}igning \textbf{R}equest}

\newacronym{ipc}{IPC}{\textbf{I}inter\textbf{P}rocess \textbf{C}ommunication}

\newacronym{oidc}{OIDC}{\textbf{O}pen\textbf{ID} \textbf{C}onnect}